---
title: "Sterling 2023 Reproduction Study"
author: "Jorre Dahl and Lucas Nerbonne"
date: "`r Sys.Date()`"
output: html_document
editor_options:
  markdown:
    wrap: sentence
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../../docs") })
nocite: '@*'
bibliography: "../../software.bib"
---

# Abstract

This study is a *reproduction* of Charles W. Sterling III et al's study on "Connections Between Present-Day Water Access and Historical Redlining".

> Sterling III, Charles W., et al. "Connections between present-day water access and historical redlining." Environmental Justice (2023). DOI:[10.1089/env.2022.0115](https://doi.org/10.1089/env.2022.0115)

This study uses ACS Census data and historical HOLC records of neighborhoods to examine the correlation of historical redlining and current-day access to water in cities. 
The study uses a binary logistic regression to identify relationships of different demographic and HOLC varaibles to access to water and sewage. 
The study finds that historically worse HOLC scores were correlated with less access to water in cities across all regions of the United States.

- `Key words`: ACS, HOLC Grade, Redlining, Water Access
- `Subject`: Social and Behavioral Sciences: Geography: Human Geography
- `Date created`: 4/7/25
- `Date modified`: 4/7/25
- `Spatial Coverage`: A collection of inner-city cores with historical HOLC grades that are stored in the University of Richmond Mapping Inequality database. 
- `Spatial Resolution`: Area-Weighted Census Blocks Clipped by HOLC zone
- `Spatial Reference System`: WGS84 EPSG:4326
- `Temporal Coverage`: 2016-2020
- `Temporal Resolution`: Observations collected yearly
- `Funding Name`: none
- `Funding Title`: none
- `Award info URI`: none
- `Award number`: none

## Original study spatio-temporal metadata

- `Spatial Coverage`: Specific inner-cities that are included in the MID HOCL Grade dataset across the United States. Data is limited to post- WW2 inner core census tracts due to the boundaries of HOLC Zones. 
- `Spatial Resolution`: resolution of original study
- `Spatial Reference System`: spatial reference system of original study
- `Temporal Coverage`: temporal extent of original study
- `Temporal Resolution`: temporal resolution of original study

# Study design

Describe how the study relates to prior literature, e.g. is it a **original study**, **meta-analysis study**, **reproduction study**, **reanalysis study**, or **replication study**?

Also describe the original study archetype, e.g. is it **observational**, **experimental**, **quasi-experimental**, or **exploratory**?

Enumerate specific **hypotheses** to be tested or **research questions** to be investigated here, and specify the type of method, statistical test or model to be used on the hypothesis or question.

This study is a *reproduction* of Charles W. Sterling III et al's study on "Connections Between Present-Day Water Access and Historical Redlining", a study which set out to 
explore the relationship between prevalence of the `complete plumbing` ACS variable in census blocks and historical neighborhood HOLC grades. In the study, Sterling hypothesizes that there will be a link
between HOLC grade and complete plumbing. This hypothesis is based on the HOLC's well documented history of assigning neighborhoods of color the lowest grades and previous findings
of a nationwide link between race and complete plumbing prevalance as found in Deitz and Meehan 2019. Sterling's work uses similar method to this study, using a logistic regression to test the link between the neighborhood grades and plumbing. 

Other methods included in this study include the use of Areal Interpolation to supposedly assign ACS variable characteristics to the HOLC graded neighborhoods. 
This is somewhat of a strange strategy; often used to fill in missing or anamolous values in gridded data, areal interpolation doesn't make a lot of sense 
for something like assigning data to an irregularly shaped polygon. Furthermore, areal interpolation assigns a value that is a average of several values of the areal units on either side of it.
This suggests that the phenomena to be studied in the filled in area is a continuation of patterns that are present proximal to it. This is almost the opposite of the point of HOLC grades,
grades assigned to neighborhoods based on their characteristics that set them apart. There's a somewhat simple explanation to why Sterling chose to use this approach; The study that Sterling cites as the published usage of this technique for re-aggregating HOLC data - Fricker and Allen 2022 - used 
area-weighted-reaggregation to re-assign casualties from tornado paths to the neighborhoods they passed through, but incorrectly used the term 'areal interpolation' to describe their method. This means that likely Sterling also just used AWR. This assumption is supported by an interrogation of the python package used for the 
reaggregation, which considers AWR "the simplest form of areal interpolation", a somewhat misleading designation given that the two refer to different techniques. 


# Materials and procedure

## Computational environment

This reproduction uses the: R packages

```{r environment-setup, include = FALSE}
# record all the packages you are using here
# this includes any calls to library(), require(),
# and double colons such as here::i_am()
packages <- c("tidyverse", "here", "tidycensus", "margins", "sf", "tigris")

# force all conflicts to become errors
# if you load dplyr and use filter(), R has to guess whether you mean dplyr::filter() or stats::filter()
# the conflicted package forces you to be explicit about this
# disable at your own peril
# https://conflicted.r-lib.org/
require(conflicted)

# load and install required packages
# https://groundhogr.com/
if (!require(groundhog)) {
  install.packages("groundhog")
  require(groundhog)
}

# this date will be used to determine the versions of R and your packages
# it is best practice to keep R and its packages up to date
groundhog.day <- "2025-04-01"

# this replaces any library() or require() calls
groundhog.library(packages, groundhog.day)
# you may need to install a correct version of R
# you may need to respond OK in the console to permit groundhog to install packages
# you may need to restart R and rerun this code to load installed packages
# In RStudio, restart r with Session -> Restart Session

# record the R processing environment
# alternatively, use devtools::session_info() for better results
writeLines(
  capture.output(sessionInfo()),
  here("procedure", "environment", paste0("r-environment-", Sys.Date(), ".txt"))
)

# save package citations
knitr::write_bib(c(packages, "base"), file = here("software.bib"))

# set up default knitr parameters
# https://yihui.org/knitr/options/
knitr::opts_chunk$set(
  echo = FALSE, # Show outputs, but not code. Change to TRUE to show code as well
  fig.retina = 4,
  fig.width = 8,
  fig.path = paste0(here("results", "figures"), "/")
)

```

## Data and variables

This study used only two data sources; American Community Survey (ACS) demographic data and maps of neighborhood's historical mortgage HOLC grades, published and maintained on
the University of Richmond's Mapping Inequality Database. 

### American Community Survey (ACS)

- `Title`: American Community Survey (ACS)
- `Abstract`: The ACS is a nationwide survey that collects and produces information on social, 
economic, housing, and demographic characteristics about our nation's population every year
- `Spatial Coverage`: United States of America
- `Spatial Resolution`: ACS data is aggregated by Census Block. 
- `Spatial Representation Type`: `vector`, `MULTIPOLYGON`
- `Spatial Reference System`: `NAD83`
- `Temporal Coverage`: ACS data from 2016-2020. 
- `Temporal Resolution`: Data is collected annually. 
- `Lineage`: Downloaded and used as-is.
- `Distribution`: Data is publically avalible from the US Census (https://www.census.gov/programs-surveys/acs/data.html)[https://www.census.gov/programs-surveys/acs/data.html]
- `Constraints`: Publicly available data.
- `Data Quality`: N/A

See acs_values.csv at `/data/raw/public/acs_values.csv`

```{r ACS Metadata}
my_vars <- c(total_pop_race = "B01003_001", white_pop = "B02008_001", black_pop = "B02009_001", ind_pop = "B02010_001", asian_pop = "B02011_001", total_pop_hisp = "B03003_001", hisp_pop = "B03003_003", total_pop_pl = "B29003_001", bp_pop = "B29003_002", total_hu_ten = "B25003_001", total_own = "B25003_002", total_rent = "B25003_003", total_hu_mh = "B25024_001", total_mh = "B25024_010", total_hu_age = "B25034_001", age_2014 = "B25034_002", age_2010 = "B25034_003", age_2000 = "B25034_004", age_1990 = "B25034_005", age_1980 = "B25034_006", age_1970 = "B25034_007", age_1960 = "B25034_008", age_1950 = "B25034_009", age_1940 = "B25034_010", age_1939 = "B25034_011", total_hu_plumb = "B25047_001", c_plumb = "B25047_002", ic_plumb = "B25047_003", total_pop_fb = "B05012_001", fb_pop = "B05012_003")

acs_vars <- load_variables(2020, "acs5", cache = TRUE)

user_guide <- acs_vars %>%
  dplyr::filter(name %in% my_vars) %>%
  select(name, label, concept)

user_guide |> write.csv(here('data','raw','public','acs_values.csv'))

user_guide
```


```{r Collect-ACS}
if (!file.exists(here('data','raw','public','acs_censusblock.gpkg')) & !file.exists(here('data','raw','public','acs_tract.gpkg'))) {
  states <- c("AL", "AZ", "AR", "CA", "CO", "CT", "DE", "FL", "GA", "ID", "IL", "IN", "IA", "KS", "KY", "LA", "ME", "MD", "MA", "MI", "MN", "MS", "MO", "MT", "NE", "NV", "NH", "NJ", "NM", "NY", "NC", "ND", "OH", "OK", "OR", "PA", "RI", "SC", "SD", "TN", "TX", "UT", "VT", "VA", "WA", "WV", "WI", "WY")
  
  options(tigris_class = "sf")
  
  all_geo <- list()
  
  for (st in states) {
    cb_geometry <- block_groups(state = st, cb = TRUE, year = 2020)
    all_geo[[length(all_geo) + 1]] <- cb_geometry
  }
  
  acs_cb <- get_acs(
    geography = "block group",
    variables = my_vars,
    state =  states,
    year = 2020,
    survey = "acs5",
    geometry = FALSE,
    output = "wide"
  )
  
  geo_cb <- do.call(rbind, all_geo)
  
  acs_cb <- acs_cb |> left_join(geo_cb, by = "GEOID")
}
```

*Unplanned Deviation* This study uses block group-level data for the foreign-born population. However, the ACS datasets have no information about place-of-birth at this level. Instead, data for foreign-born population percentage is gathered at the tract level.

```{r ud-tract-acs}
if (!file.exists(here('data','raw','public','acs_censusblock.gpkg')) & !file.exists(here('data','raw','public','acs_tract.gpkg'))) {
  all_geo_t <- list()
  
  for (st in states) {
    t_geometry <- tracts(state = st, cb = FALSE, year = 2020)
    all_geo_t[[length(all_geo_t) + 1]] <- t_geometry
  }
  
  acs_t <- get_acs(
    geography = "tract",
    variables = c(total_pop_fb = "B05012_001", fb_pop = "B05012_003"),
    state =  states,
    year = 2020,
    survey = "acs5",
    geometry = FALSE,
    output = "wide"
  )
  
  geo_t <- do.call(rbind, all_geo_t)
  
  acs_t <- acs_t |> left_join(geo_t, by = "GEOID")
}
```

``` {R write-acs-to-private}
if (!file.exists(here('data','raw','public','acs_censusblock.gpkg')) & !file.exists(here('data','raw','public','acs_tract.gpkg'))) {
  acs_cb |> write_sf(here('data','raw','private','acs_censusblock.gpkg'))
  
  acs_t |> write_sf(here('data','raw','private','acs_tract.gpkg'))
}
```

### HOLC Grades

 `Title`: HOLC grades from the Mapping Inequality Database (MID)
- `Abstract`: HOLC grades are historical neighborhood delineations created by the Home Owners’ Loan Corporation in the 1930s to assess mortgage lending risk. These maps were used to guide investment and disinvestment in urban areas
 and are a foundational dataset for understanding redlining and its long-term impacts.
- `Spatial Coverage`: Select major U.S. cities
- `Spatial Resolution`: Neighborhood-scale boundaries (city block to district level, variable by city)
- `Spatial Representation Type`: `vector`, `MULTIPOLYGON`
- `Spatial Reference System`: `NAD83`
- `Temporal Coverage`: 1935–1940 (approximate dates of HOLC map creation)
- `Temporal Resolution`: Single mapping effort. 
- `Lineage`: Downloaded and used as-is.
- `Distribution`: Data is avalible on the Mapping Inequality website (https://dsl.richmond.edu/panorama/redlining/data)[https://dsl.richmond.edu/panorama/redlining/data]
- `Constraints`: Publicly available data under a [CC-by-NC 2.5 license](https://creativecommons.org/licenses/by-nc/2.5/deed.en)
- `Data Quality`: Accurate to the degree that the original digitization of the 1930's HOLC maps was accurate. 

| Label | Alias | Definition | Type | Accuracy | Domain | Missing Data Value(s) | Missing Data Frequency |
| :--: | :--: | :--: | :--: | :--: | :--: | :--: | :--: |
| city | City Name | City in which the HOLC designated area resides | character | N/A | Names of US cities | none | none |
| state | State Abbreviation | USPS state designator | character | N/A | The 50 states | N/A | none |
| category | Desirability | Assessment of investment desirability based on HOLC designation  | character | subjective/historical | a range of desigations | none | none |
| grade | Grade | Historical HOLC grade | character | subjective/historical | A - D | none | none |
| label | Shape Label | HOLC grade and arbitrary number (A1, C3) to divide same-grade areas from the same city| character | N/A | A-D, number of same-grade zones in the same city | none | none |
| residential | Is it residential? | " " | binary (TRUE/FALSE) | N/A | TRUE/FALSE | none | none |
| commercial | Is it commercial? | " "  | binary (TRUE/FALSE) | N/A | TRUE/FALSE | none | none |
| industrial | Is it industrial? | " "  | binary (TRUE/FALSE) | N/A | TRUE/FALSE | none | none |

*Unplanned Deviation* Not all HOLC polygons have valid geometry, so invalid geometry was fixed by splitting to single parts before performing the intersects function

```{r Collect-HOLC}
holc_polygons<- st_read(here("data", "raw", "public", "mappinginequality.gpkg"), layer = "mappinginequality", quiet = TRUE)
holc_polygons<- st_transform(holc_polygons, 4269)

holc_polygons_fixed <- st_make_valid(holc_polygons)

holc_polygons_fixed$isvalid <- st_is_valid(holc_polygons)

holc_polygons_bugged <- holc_polygons_fixed |>
  dplyr::filter(isvalid == FALSE)

holc_polygons_fixed <- holc_polygons_fixed |>
  dplyr::filter(isvalid == TRUE)

holc_polygons_singlepart <- st_cast(holc_polygons_bugged, "POLYGON")

holc_polygons_singlepart <- st_make_valid(holc_polygons_singlepart)

holc_polygons_singlepart$isvalid <- st_is_valid(holc_polygons_singlepart)

holc_polygons_singlepart <- holc_polygons_singlepart |>
  dplyr::filter(isvalid == TRUE)

holc_polygons_fixed <- holc_polygons_fixed |>
  rbind(holc_polygons_singlepart)
```

In order to first save data, the tract and census block data should first be intersected by these HOLC polygons

```{r Clip-acs}
if (!file.exists(here('data','raw','public','acs_censusblock.gpkg')) & !file.exists(here('data','raw','public','acs_tract.gpkg'))) {
  cb_intersection_indeces <- st_intersects(st_make_valid(st_as_sf(acs_cb)), holc_polygons_fixed)
  
  t_intersection_indeces <- st_intersects(st_as_sf(acs_t), holc_polygons_fixed)
  
  cb_non_empty_indeces <- which(lengths(cb_intersection_indeces) > 0)
  cb_intersects <- acs_cb[cb_non_empty_indeces, ]
  
  t_non_empty_indeces <- which(lengths(t_intersection_indeces) > 0)
  t_intersects <- acs_t[t_non_empty_indeces, ]
}
```

```{r rejoin-holc}
holc_polygons_fixed <- holc_polygons_fixed |>
    group_by(area_id,city,state,city_survey,category,grade,label,residential,commercial,industrial,fill) |>
    summarize(geom = st_union(geom))
```

```{r write-census-public}
if (!file.exists(here('data','raw','public','acs_censusblock.gpkg')) & !file.exists(here('data','raw','public','acs_tract.gpkg'))) {
  cb_intersects |> write_sf(here('data','raw','public','acs_censusblock.gpkg'))
  
  t_intersects |> write_sf(here('data','raw','public','acs_tract.gpkg'))
}
```

```{r load acs data public}
cb_intersects<- st_read(here('data','raw','public','acs_censusblock.gpkg'))
t_intersects<- st_read(here('data','raw','public','acs_tract.gpkg'))
```
## Prior observations  

There are no prior observations related with this data.

## Bias and threats to validity

Three main source of bias in this study come from the HOLC data itself.
Firstly, the spatial extent of the HOLC data only covers the centers of major cities across the united states, limiting the analysis to center-cities. 
Secondly, 'Areal Interpolation' was used to determine census data values for each HOLC neighborhood, a method that doesn't seem logical or advisable give the study context. Some data in the study suggests that this actually was a more logical area weighted reaggregation.
Choosing individual HOLC polygons as the study's resolution increases the threat to validity through the Modifiable Areal Unit Problem. Many of the polygons represent outdated neighborhood lines, and are limited only to populated areas from that time period. This affects the data being used to represent each neighborhood today, especially considering that area-weighted reaggregation is being used.

## Data transformations

First, remap ACS values from block groups to HOLC polygons through areal interpolation, likely actually area-weighted reaggregation. 

```{r remap values}
cb_intersects <- cb_intersects |>
  mutate(area = st_area(geom))

t_intersects <- t_intersects |>
  mutate(area = st_area(geom))

cb_clipped <- st_intersection(cb_intersects, holc_polygons_fixed) |>
  mutate(area_clipped = st_area(geom),
         awr = area_clipped / area)

t_clipped <- st_intersection(t_intersects, holc_polygons_fixed) |>
  mutate(area_clipped = st_area(geom),
         awr = area_clipped / area)

ACS_clipped <- ACS |>
  st_intersection(HOLC) |>
  mutate(area_clipped = st_area()) |>
  select(fips, area_clipped) |>
  st_drop_geometry()

ACS_combined <- left_join(ACS, ACS_clipped, by = "GeoID")
ACS_scaled <- ACS_combined|>
mutate(area_ratio = area/area_clipped)|>
mutate(V1 = V1/area_ratio,
       V2 = V2 ...
       )

ACS_for_joining <- st_join(ACS_combined, HOLC[, holc_id], join = st_intersects)
HOLC_aggregated <- ACS_for_joining|>
groupby(HOLC$someidentifier)|>
summarise(total_V1 = sum(V1, na.rm = TRUE),
total_V2 = sum(V1, na.rm = TRUE), 
...
)

```

Using census statistics from the ACS dataset, resulting calculated assigned variables are: Black Population %, White Population %, Indigenous American %, Asian  Population %, Hispanic or Latino Population %, % Below Poverty Line, % Housing Units Owned, % Housing Units Rented, % Mobile Homes, % Homes before 1980, % Homes after 1980, % With Complete Plumbing, % With Incomplete Plumbing, and % Foreign Born. This data is separated by region as well as collected nationally. Using regional and national averages for plumbing rates, a binary variable is calculated on whether plumbing is below or above the average.

```{bianary creation}
HOLC_aggregated <- HOLC_aggregated |>
  mutate(
    water_access = case_when(
      `% With Incomplete Plumbing` > 2.61668 ~ 1,
      TRUE ~ 0
    )
  )

data_clean <- HOLC_aggregated |>
  select(
    holc_id,
    holc_grade
    neighborho,
    area_descr,
    `Black Population %`,
    `White Population %`,
    `Indigenous American %`,
    `Asian Population %`,
    `Hispanic or Latino Population %`,
    `% Below Poverty Line`,
    `% Housing Units Owned`,
    `% Housing Units Rented`,
    `% Mobile Homes`,
    `% Homes before 1980`,
    `% Homes after 1980`,
    `% With Complete Plumbing`,
    `% With Incomplete Plumbing`,
    `% Foreign Born`,
    Shape_Area,
    water_access
  )

```

Data will now be verified using the supplementary tables by subtracting them from the calculated data, which should result in zeros across the board. 
This is somewhat of a test of whether the authors actually did in fact use area weighted reaggregation or areal interpolation; if they used AWI, our results should match.
Additionally, because the reaggregation was done in a Python package this will test the similarities/differences of our implementation. 

This is somewhat of a test of whether the authors actually did in fact use area weighted reaggregation or areal interpolation; if they used AWI, our results should match.
Additionally, because the reaggregation was done in a Python package this will test the similarities/differences of our implementation. 

The chosen method to test the accuracy of the data is to compare it to the regional summary statistics, presented in table 1 (results/tables/original/table_1.csv). I'll split data_clean rows into regions, 
calculate summary stats for them, compile into a single df, and then subtract them from table 1. 

```{test AWI}
sd_midwest<- read_csv("data/derived/public/original/sd_midwest.csv")
sd_northeast<- read_csv("data/derived/public/original/sd_northeast.csv")
sd_south<- read_csv("data/derived/public/original/sd_south.csv")
sd_west<- read_csv("data/derived/public/original/sd_west.csv")

sd_midwest_testing <- sd_midwest[, 2:ncolumn(sd_midwest)]
sd_midwest_testing <- sd_northeast[, 2:ncolumn(sd_northeast)]
sd_midwest_testing <- sd_south[, 2:ncolumn(sd_south)]
sd_midwest_testing <- sd_west[, 2:ncolumn(sd_west)]



data_test <- data_clean %>% select(-holc_grade)
test1<- data_test-national_testing

kbl(test1) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = TRUE) %>%
  scroll_box(width = "100%", height = "400px")
```

Then, use the Dunn Test to determine whether incomplete plumbing % in Grade A is significantly different than the other Grades and compared with supplementary table 1.

```{dunn test}
Dunntest<- dunnTest(`% With Incomplete Plumbing` ~ holc_grade, data = data_clean) #dunn test
original_dunn_results<- st_read("results/tables/original/table_s1.csv")
test2<- (Dunntest - original_dunn_results) #subtracting for comparison

kbl(test2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = TRUE) %>%
  scroll_box(width = "100%", height = "400px")
```

Using a Stepwise function with the $StepAIC$ package and the HOLC Grade A as a reference group, we can gather a correlation table to remove the highest correlation values. In this case, the highest correlation value will be removed, and compared with supplementary table 2.

## Analysis

Sterling III's original study used a binary logistic regression model to compare categorical hold grades and a census block group's binary desigantion of whether plumbing rates were above or below average. Results were gathered as the Average Marginal Effects (AME) of different census-derived varaibles represented as binary values.

# Results

Data is presented as 3 figures, 2 tables, and 7 supplementary tables:

Figures:

- Map of HOLC grades for different cities across regions
- Correlation plot for potential predictive variables
- Map of percent of houses with incomplete plumbing  across regions

Tables:

- Average Marginal Effects of Variables determined by Binary Regression Model
- The Number of Each Grade Polygon in Each Data Set

Supplementary Tables:

- The results of the Dunn Test to determine whether incomplete plumbing % in Grade A is significantly different than the other Grades
- The average % for each predictive variable broken down by HOLC grade and region
- AME Table for the Nation using the average 2.61168 as the threshold for the binary variable

National Data Tables
- AME Table for the Northeast region using the average 1.447623 as the threshold for the binary variable
- AME Table for the South region using the average 3.414391 as the threshold for the binary variable
- AME Table for the Midwest region using the average 3.756471 as the threshold for the binary variable
- AME Table for the West region using the average 0.7836609 as the threshold for the binary variable

# Discussion

Sterling III hypothesizes that areas of present-day incomplete plumbing within U.S. cities (i.e., communities with a proportion of homes lacking complete plumbing above the national average) are significantly associated with HOLC neighborhood designations. The study finds evidence for this hypothesis.

A successful reproduction would confirm this hypothesis with similar derived values to those found in the original study.

# Integrity Statement

The authors of this preregistration state that they completed this preregistration to the best of their knowledge and that no other preregistration exists pertaining to the same hypotheses and research.

# Acknowledgements

This report is based upon the template for Reproducible and Replicable Research in Human-Environment and Geographical Sciences, DOI:[10.17605/OSF.IO/W29MQ](https://doi.org/10.17605/OSF.IO/W29MQ)

# References

> Sterling III, Charles W., et al. "Connections between present-day water access and historical redlining." Environmental Justice (2023). DOI:[10.1089/env.2022.0115](https://doi.org/10.1089/env.2022.0115)

> Shiloh Deitz and Katie Meehan. “Plumbing Poverty: Mapping Hot Spots of Racial and Geographic Inequality in U.S. Household Water Insecurity.” Annals of the American Association of Geographers 109 (2019): 1092–1109.

> Tyler Fricker and Douglas L. Allen. “A Place-Based Analysis of Tornado Activity and Casualties in Shreveport, Louisiana.” Natural Hazards 113 (2022): 1853–1874.
